\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-12 jss/article.tex
reference
baseball pic

Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j}), ~j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger). This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.

\subsection{Binomial: 18 Baseball Data}
This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975). Also, it has one binary covariate indicating whether a player was in the National league (1) or in the American league (0). The code below shows a way to make inputs using the first 10 players. If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  0,  0,  0,  0,  0,  1,  0,  1,  1) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown parameter $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

@@

\section[Reference]{Reference}
Christiansen, C. and Morris, C. (1996). ``Fitting and Checking a Two-Level Poisson Model: Modeling Patient Mortality Rates in Heart Transplant Patients,'' in \emph{Bayesian Biostatistics}, eds. D. Berry and D. Stangl, New York: Marcel Dekker, pp. 467-561.
\\
Efron, B. and Morris, C. (1975). ``Data Analysis Using Stein's Estimator and its Generalizations.'' \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
\\
Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
\\
Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
\\
Rubin, D. B. (1981). ``Estimation in parallel randomized
  experiments.'' \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.
\\

>>>>

Considering the type of data, it makes sense to assume the number of deaths in each hospital has independent Poisson distribution given the unknown parameter $\lambda_{j}$: $z_{j}\vert \lambda_{j}\stackrel{ind}{\sim} \textrm{Poisson}(n_{j}\lambda_{j})$, $j=1, \ldots, 31,$ where $n_{j}$ can be interpreted as an exposure (not necessarily an interger). This dataset is also included in the package and can be called by `\code{R> data(hospital)}' on \proglang{R}.

\subsection{Binomial: 18 Baseball Data}
This dataset contains information about batting averages of 18 major league players through their first 45 official at-bats of the 1970 season (Efron and Morris, 1975). Also, it has two covariates, League and Position, showing in which league and in which position each player was. In this paper, we will use Position for a tutorial purpose. For convenience, we transform this variable into a binary indicator, which is 1 if a player was a outfielder and 0 otherwise. The code below shows a way to make inputs. If we have more than one covariate, for example, \code{x1} and \code{x2}, then `\code{R> x <- cbind(x1, x2)}' will be the right input of the \code{gbp} function.
\begin{CodeChunk}
\begin{CodeInput}
R> z <- c(18, 17, 16, 15, 14, 14, 13, 12, 11, 11, 10, 10, 10, 10, 10,  9,  8,  7)
R> n <- c(45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45, 45)
R> x <- c( 1,  1,  1,  1,  1,  0,  0,  0,  0,  1,  0,  0,  0,  1,  1,  0,  0,  0) 
\end{CodeInput}
\end{CodeChunk}
The data indicate that independent Binomial distribution is appropriate for each player's number of hits among 45 at-bats conditioning on the unknown parameter $p_{j}$: $z_{j}\vert p_{j}\stackrel{ind}{\sim} \textrm{Binomial}(n_{j}, p_{j}), ~j=1, \ldots, 18$. This dataset is also a part of the package and can be called on \proglang{R} by `\code{R> data(baseball)}'.

@@

\section[Reference]{Reference}
Christiansen, C. and Morris, C. (1996). ``Fitting and Checking a Two-Level Poisson Model: Modeling Patient Mortality Rates in Heart Transplant Patients,'' in \emph{Bayesian Biostatistics}, eds. D. Berry and D. Stangl, New York: Marcel Dekker, pp. 467-561.
\\

Efron, B. and Morris, C. (1975). ``Data Analysis Using Stein's Estimator and its Generalizations.'' \emph{Journal of the American Statistical Association}. \textbf{70}. 311-319.
\\

Kass, R. and Steffey, D. (1989). ``Approximate Bayesian Inference in Conditionally Independent Hierarchical Models (Parametric
Empirical Bayes Models).'' \emph{Journal of the American Statistical Association}. \textbf{84}. 717-726.
\\

Morris, C. and Tang, R. (2011). ``Estimating Random Effects via Adjustment for Density Maximization.'' \emph{Statistical Science}. \textbf{26}. 271-287.
\\

Morris, C. and Lysy, M. (2012). ``Shrinkage Estimation in Multilevel Normal Models.'' \emph{Statistical Science}. \textbf{27}. 115-134.
\\

Rubin, D. B. (1981). ``Estimation in parallel randomized
  experiments.'' \emph{Journal of Educational Statistics}. \textbf{6}. 377-401.
\\
